---
title: "GBD and energy"
author: "Guillaume Chevance, Baptiste Andrieu"
date: "February 2023"
output:
  pdf_document:
    toc: yes
  word_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
    theme: cerulean
---

## SET-UP (libraries necessary to run code)

```{r message=FALSE}
install.packages(c("metafor", "dplyr","readxl", "ggplot2","xlsx"))
library(metafor)
library(dplyr)
library(readxl)
library(ggplot2)
library(xlsx)
#getwd()
#setwd("C:/Users/...")
```

# Meta analysis per disease
```{r message=FALSE}
  

for (indicator in c("incidence", "prevalence", "YLDs", "YLLs"))
{
  data <- read_excel(paste("results/data_for_ma_",indicator,".xlsx",sep=""),sheet = 'all_years')
  mydata <- data.frame(row.names =  c(paste('all_y','estimate'),paste('all_y','se'),paste('all_y',"ci.lb"),paste('all_y',"ci.ub"),paste('all_y',"pval")))
for (i in as.list(unique(data$mod)))
  {
    ma<-rma(rvalue, sei=stderr, data=data, subset = mod==i)
    mylist = c(ma['b'][[1]][1],ma[['se']],ma[['ci.lb']],ma[['ci.ub']],ma[['pval']])
    mydata <- cbind(mydata, i = mylist)
    names(mydata)[names(mydata)=="i"]<-i
  }
  df <- t(mydata)
  for (year in c(seq(1990,2019)))
  {
    data <-read_excel(paste("results/data_for_ma_",indicator,".xlsx",sep=""),sheet = as.character(year))
    mydata <- data.frame(row.names = c(paste(year,'estimate'),paste(year,'se'),paste(year,"ci.lb"),paste(year,"ci.ub"),paste(year,"pval")))
    for (i in as.list(unique(data$mod)))
    {
      ma<-rma(rvalue, sei=stderr, data=data, subset = mod==i,control=list(stepadj=0.5, maxiter=10000))
      mylist = c(ma['b'][[1]][1],ma[['se']],ma[['ci.lb']],ma[['ci.ub']],ma[['pval']])
      mydata <- cbind(mydata, i = mylist)
      names(mydata)[names(mydata)=="i"]<-i
    }
    df <-cbind(df,t(mydata))
  }
  write.xlsx(data.frame(df),paste("results/ma_results_",indicator,".xlsx",sep=""),col.names = TRUE, row.names = TRUE)
}



'''